Contextuality and the Born rule in fuzzy quantum theories

### 2017-04-07 prop_letter.tex
prop_letter.tex \paragraph{Quantum IVPM and Real-valued Probability Measure} Updating...

In the language of core, Gleason's theorem states that $\mathrm{core}\left(\bar{\mu},\events\right)$
has a unique element for any quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$
when $d\ge3$.

@@

Recall we model the idea of the finite precision measurement as IVPM.
When we made finite number of observations, we can use some quantum
IVPMs to represent what we observed. Given a quantum IVPM~$\bar{\mu}$,
the question is whether we can refine precisely enough to determine
the underlying unknown quantum real-valued probability measure, i.e.,
a quantum state. If we can, we say $\bar{\mu}$ has a non-empty core.
More precisely, A \emph{core} of $\bar{\mu}$, $\mathrm{core}\left(\bar{\mu}\right)$,
is the set 
\begin{equation}
\set{\pmeas:\events\rightarrow[0,1]}{\forall P\in\events.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}\textrm{ .}
\end{equation}
For example, we can add an one extra interval~$\unknown=\left[0,1\right]$
to $\mathscr{I}_{\mathrm{D}}$, and consider $\mathscr{I}_{1}=\left\{ \imposs,\unknown,\necess\right\} $.
Let 
\begin{equation}
\iota_{1}(x)=\begin{cases}
\necess & \text{, if }x=1\text{ ;}\\
\imposs & \text{, if }x=0\text{ ;}\\
\unknown & \text{, otherwise.}
\end{cases}\label{eq:homomorphism-1}
\end{equation}
Then, $\iota_{1}\circ\mu_{\ket{0}}^{\mathrm{B}}:\events\rightarrow\mathscr{I}_{1}$
is a quantum IVPM whose core has a unique element~$\mu_{\ket{0}}^{\mathrm{B}}$,
where $\circ$ denote function composition.

However, not every quantum IVPM well represents our observations.
The following example provides a quantum IVPM with an empty core,
i.e., it cannot be further refined to get the underlying unknown quantum
states.

\begin{example}[Four-dimensional quantum three-interval-valued probability
measure]\label{ex:four-dimensional-three-value}Consider the orthonormal
basis~$\left\{ \ket{00},\ket{01},\ket{10},\ket{11}\right\} $ as
defined in Table~\ref{table:commonBasis}. Then, we can define a
quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{1}$ as follow:
\begin{eqnarray*}
 &  & \imposs=\bar{\mu}(\mathbb{0})=\bar{\mu}(P_{00})=\bar{\mu}(P_{0\ps})=\bar{\mu}(P_{\ps0})\textrm{ ,}\\
 &  & \necess=\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-P_{00})=\bar{\mu}(\mathbb{1}-P_{0\ps})=\bar{\mu}(\mathbb{1}-P_{\ps0})\textrm{ ,}\\
 &  & \unknown=\bar{\mu}(P)\qquad\textrm{otherwise.}
\end{eqnarray*}

To verify $\bar{\mu}$ is a quantum IVPM, first notice that $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
implies equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
by induction. Second, equation (\ref{eq:QuantumInterval-valuedProbability-Complement})
implies $\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(P\right)+\bar{\mu}\left(\mathbb{1}-P\right)$.
Therefore, to prove equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
it is sufficient to check \begin{subequations} 
\begin{eqnarray}
 &  & \bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)\nonumber \\*
 & \subseteq & \bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)\textrm{ ,}\\
 &  & \bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}+\proj{\psi_{2}}\right)\nonumber \\*
 & \subseteq & \bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)
\end{eqnarray}
\end{subequations} for orthogonal $\ket{\psi_{0}}$, $\ket{\psi_{1}}$,
and $\ket{\psi_{2}}$. These equation always hold because $\unknown$
is a subset of the left-hand side of both of the equations.

>>>>

In the language of core, Gleason's theorem states that $\mathrm{core}\left(\bar{\mu},\events\right)$
has a unique element for any quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$
when $d\ge3$. However, when we only have finite resources, a quantum
IVPM may be identified to more than one states on different sub-event
spaces. The simplest example add an one extra interval~$\unknown=\left[0,1\right]$
to $\mathscr{I}_{\mathrm{D}}$, and consider $\mathscr{I}_{1}=\left\{ \imposs,\unknown,\necess\right\} $.
Then, 
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\necess & \text{, if }P=\mathbb{1}\text{ ;}\\
\imposs & \text{, if }P=\mathbb{0}\text{ ;}\\
\unknown & \text{, otherwise.}
\end{cases}\label{eq:homomorphism-1}
\end{equation}
provides no information about any results so that $\mathrm{core}\left(\bar{\mu}_{1},\events'\right)$
contains every quantum real-valued probability measure on $\events'$.
The following is a more sophisticating example.

\begin{example}[Four-dimensional quantum three-interval-valued probability
measure]\label{ex:four-dimensional-three-value}Consider the orthonormal
basis~$\left\{ \ket{00},\ket{01},\ket{10},\ket{11}\right\} $ as
defined in Table~\ref{table:commonBasis}. Let
\begin{eqnarray*}
 &  & \imposs=\bar{\mu}(\mathbb{0})=\bar{\mu}(P_{00})=\bar{\mu}(P_{0\ps})=\bar{\mu}(P_{\ps0})\textrm{ ,}\\
 &  & \necess=\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-P_{00})=\bar{\mu}(\mathbb{1}-P_{0\ps})=\bar{\mu}(\mathbb{1}-P_{\ps0})\textrm{ ,}\\
 &  & \unknown=\bar{\mu}(P)\qquad\textrm{otherwise.}
\end{eqnarray*}
It is straightforward to verify that $\bar{\mu}$ is a quantum IVPM.

@@
